\textbf{\sffamily\Huge \ShortTitle}\\ {\textbf{\sffamily\Large \FullTitle}} \vspace{1cm}

### 2014-12-11 proposal/sections/method.tex

\section{Method}
\label{sect:method}

\note{
\begin{itemize}
\item {\em Length: 2-5 pages}
\item {\bf How?}
\item How should the expected results be achieved?
\item What method(s) will be applied? (e.g., empirical study, user-centered design, prototype implementation,...)
\item Description of the methods.
\item Justifications for chosen methods.
\end{itemize}
}

>>>>

\section{Method}
\label{sect:method}
\subsection{How should the expected results be achieved?}
In the first place some basic research about brain waves should be done in order to achieve the expected results and build a device for brain wave based authentication. The goal of the projects research part is to clarify the scientific requirements needed for the creation of the prototype, for example to confirm the uniqueness of brain waves or define how specific brain waves of a person can be identified. This is important since we want to assure that the user can be identified as the same one later again. It should be guaranteed that thoughts provide a reliable identification method, therefore the research should give answers how reliably brain waves of a person can be identified.

The research part consists of two phases – a theoretical and an empirical research part. The purpose of the theoretical part is to analyse existing studies and use the results for the project. Already existing studies confirmed the possibility of authentication via brain waves, but so far no study managed to measure brain waves from different head parts than the forehead. The studies showed theoretical approaches to measure brain waves using EEG electrodes placed at the users forehead. The goal of the theoretical research part is to use this approaches and sensor minimising methods in order to define requirements for building a small device, called Wavy. Therefore, the goal to measure brain waves from different head or even body parts is a very important part of the research. The Wavy device should be as small as possible and designed in a way which allows the user to wear it in everyday life. The ears will be the primary focus of this research for measuring brain waves at positions less visible then the forehead. This will enable the Wavy device to be worn like an accessory on or behind the ear.

In the empirical part there will be some practical tests with human beings, where their brain waves will be measured with an EEG in different situations. The goal of this research part is to confirm the uniqueness of two peoples brain waves, even if they think about the same thing. The approach from UC Berkeley, which John Chuang presented at the 17th International Conference on Financial Cryptography and Data Security, is a good one to use for the project. In this approach the participants were asked to perform seven mental tasks. These were divided into two categories. For the first group of tasks - which was the same for all participants - the subjects were asked to do simple things, for example to focus on their own breathing, imagine moving a finger, or to listen for an audio tone and respond to that by focusing on a dot on a piece of paper. For the second group of tasks - which participants selected and performed individually without letting others know what they were doing - the subjects were asked to select from imagining performing a repetitive motion from their favourite sport, such as swinging a golf club; singing a song of their choice; watch a series of on-screen objects and silently count those that matched a color of their choice; or think of something for 10 seconds. \cite{Adhikari13} With such tests the Berkeley researchers managed to ensure that brain waves provide enough information to authenticate the user's identity. This kind of tests will be also done with users in our empirical research part once the prototype will be constructed.

\subsection{What methods will be applied?}
The following methods will be used:

\subsubsection{Theoretical study}
The goal of the theoretical study is to gather information from existing studies on this field. Several different studies already investigated the possibility of using brain waves as access method. Their findings will be used as a start point for our research. Researchers in the field of neuroscience and computer science will be needed for this task which will be part of the first work packages at the beginning of the project.

\subsubsection{Experiments}
This part consists of performing practical tests with participants. During these tests the users will wear an EEG device and will be asked to think of some simple things as well as thinking of some personal memories or for example their favourite song. The experiments will define whether brain waves of every single person are unique and how reliable they can be measured from different body parts. The participants will have to be selected as heterogeneous group so that the experiments can be performed on people with different characteristics such as male/female, adult/children, etc. Again the neuroscience and computer science are the required fields of expertise for this part.

\subsubsection{Prototype}
In order to get to this project phase the first phase which includes the brain wave connected research part should be completed. The goal of this phase is to use the results from the research part and create the Wavy prototype and write a demo software. The Wavy should be as small as possible and communicates with the user's device via Bluetooth. It listens for a brain wave pattern that was previously trained by the user as a password. If the correct pattern was detected by the Wavy it transmits a OK signal back to the client device. A demonstration software shall be written to show how the Wavy device can be used. This work will require an hardware and a software engineer to work together with the researchers.

\subsubsection{Scientific study}
At the end of the project the security and usability of authenticating via the Wavy device will be compared to existing authentication methods. This study should generate a comprehensive report which can be published to show the advantages of this new authentication method and raise the public's awareness for it.

### 2014-12-11 proposal/sections/timeplan.tex

\section{Time plan (Gantt chart)}
\label{sect:timeplan}

\note{
\begin{itemize}
\item {\em Length: 1-2 pages}
\item Realistic estimation of schedule based on workpackages.
\item Including milestones (not only when but also what is to be achieved for each milestone).
\item Generation of a Gantt chart. (Including phases, milestones, buffer times, critical areas, etc.)
\end{itemize}
}

>>>>

\section{Time plan (Gantt chart)}
\label{sect:timeplan}
As specified in section 7, the project consists of three basic work packages (each of them having several sub-packages):
\begin{itemize}
\item WP 1 - Basic research
\item WP 2 - Hardware and software development
\item WP 3 - Prototype development
\end{itemize}

\begin{figure}[H]
	\centering
    \includegraphics[width=1\textwidth]{gantt_chart}
    \caption{GANTT Chart}
\end{figure}

Each of these packages consists of another sub-packages. Since the research part of the project delivers the basis for the whole project and therefore is the most important part of the project, it has a planned duration of 1,5 years. The planned duration of the hardware and software development package is 1 year and the duration of the prototype development package 1 year. Also there is a scheduled time buffer of one month in each package, which can be used in potential problematic situations and in cases of time delays appearances.

\subsection{Milestones}
The planned milestones of the projects are:
\begin{itemize}
\item 05.07.2015 - Confirmed uniqueness of a person’s brain wave pattern
\item 05.07.2016 - Research part completed 
\item 05.01.2017 - Hardware and Software for Microcontroller finished
\item 05.06.2017 - Hardware Part Completed 
\item 05.02.2018 - Prototype Completed 
\item 05.07.2018 - Project Completed 
\end{itemize}

\subsection{Timeplan}
The estimation of the schedule based on work packages:

\subsubsection{WP1 - Basic research}
\begin{itemize}
\item start date: 05.01.2015
\item end date:  05.07.2016
\item milestone: Research part completed
\end{itemize}

\subsubsection{WP 1.1 - Confirm uniqueness of a person’s brain wave pattern}
\begin{itemize}
\item start date: 05.01.2015
\item end date: 05.07.2015
\item milestone: Confirmed uniqueness of a person’s brain wave pattern
\end{itemize}
\subsubsection{WP 1.2 - Reliable thought identification}
\begin{itemize}
\item start date: 05.07.2015
\item end date:  05.01.2016
\end{itemize}
\subsubsection{WP 1.3 - Measuring methods of brain waves from different parts of the head}
\begin{itemize}
\item start date: 05.01.2016
\item end date: 05.07.2016
\end{itemize}
\subsubsection{WP 1.4 - Survey of state of the art for sensors and devices for brain wave measurement}
\begin{itemize}
\item start date: 05.01.2015
\item end date: 05.01.2016
\end{itemize}
\subsubsection{WP 2 - Hardware and software development}
\begin{itemize}
\item start date: 05.07.2016
\item end date:  05.07.2017
\end{itemize}

The Milestones for the work packages 2.2, 2.3 and 2.4 share the same milestone - Hardware and Software for Microcontroller finished and after this three work packages there is also planned a buffer of one month for eventual time delays.

\subsubsection{WP 2.1 - Reviewing of existing algorithms for detecting patterns in measured brain}
\begin{itemize}
\item start date: 05.07.2016
\item end date:  05.10.2016
\end{itemize}
\subsubsection{WP 2.2 - Develop new algorithms for detecting patterns in measured brain waves}
\begin{itemize}
\item start date: 05.10.2016
\item end date:  05.01.2017
\item milestone: Hardware and Software for Microcontroller finished 
\end{itemize}
\subsubsection{WP 2.3 - Define the communication protocol and interface of the Wavy}
\begin{itemize}
\item start date: 05.07.2016
\item end date:  05.07.2017
\item milestone: Hardware and Software for Microcontroller finished 
\end{itemize}
\subsubsection{WP 2.4 - Develop small sensors for brain wave measurement}
\begin{itemize}
\item start date: 05.07.2016
\item end date: 05.01.2017
\item milestone: Hardware and Software for Microcontroller finished 
\end{itemize}
\subsubsection{WP 2.5 - Develop a microcontroller for the Wavy}
\begin{itemize}
\item start date: 05.01.2017
\item end date: 05.07.2017
\item milestone: Hardware Part Completed
\end{itemize}
\subsubsection{WP 3 - Prototype development}
\begin{itemize}
\item start date: 05.07.2017
\item end date: 05.07.2018
\item milestone: Project Completed
\end{itemize}
\subsubsection{WP 3.1  - Create the Wavy prototype}
\begin{itemize}
\item start date: 05.07.2017
\item end date: 05.03.2018
\item milestone: Prototype Completed
\end{itemize}
\subsubsection{WP 3.2  - Write a software prototype}
\begin{itemize}
\item start date: 05.07.2017
\item end date: 05.03.2018
\item milestone: Prototype Completed
\end{itemize}
\subsubsection{WP 3.3  - Comparing with existing authentication methods}
\begin{itemize}
\item start date: 05.03.2018
\item end date:  05.07.2018
\end{itemize}

\subsection{Critical Areas}
The critical areas of this project are in the research part, because if the research parts doesn’t deliver the following results, the project will not fail but it won’t lead to the planned project goals. The Work package 1.1 (Confirm uniqueness of a person’s brain wave pattern) and 1.3 (Identify the methods to measure brain waves from different head parts) are the most critical parts of the project.

### 2014-12-11 proposal/sections/workplan.tex
remove note from tex.

\note{
\begin{itemize}
  \item {\em Length: 2-4 pages}
  \item Structuring the project into self-contained parts.
  \item Additional verbal descriptions.
  \item Work packages
  \begin{itemize}
    \item title
    \item goal(s)
    \item description
    \item expected results
    \item responsible person(s)
    \item dependencies
  \end{itemize}
\end{itemize}
}

\subsection{Basic research}
\begin{itemize}
 \item goal(s): The goal of the research part is to clarify the scientific requirements, needed for the creation of the prototype.
 \item description: This work package deals with the brain waves related part of this project.
 \item expected results: Thought identification, confirmation of the uniqueness of brain waves, measuring brain waves from different body parts.
 \item responsible person: Neuroscience researcher
 \item dependencies: none
 \item start date: 05.01.2015
 \item end date: 05.07.2016
\end{itemize}

\subsubsection{Confirm uniqueness of a person’s brain wave pattern}
\begin{itemize}
 \item goal(s): Confirm assumption of persons unique brain waves.
 \item description: Every person has an unique brain wave pattern for the same thought. This pattern can be used to identify the person.
 \item expected results: If the research shows unexpected results and it the uniqueness can’t be proved, it will limit the security aspect of the project, but it still can be realised.
 \item responsible person: Neuroscience researcher
 \item dependencies: none
 \item start date: 05.01.2015
 \item end date: 05.07.2015
\end{itemize}

\subsubsection{Reliable thought identification}
\begin{itemize}
 \item goal(s): Confirmation of our assumption, that a thought of a person can be identified again as the same.
 \item description: Research on how a specific brain wave of a person can be identified reliably.
 \item expected results: A person can be identified again as the same.
 \item responsible person: Neuroscience researcher
 \item dependencies: WP 1.1
 \item start date: 05.07.2015
 \item end date: 05.01.2016
\end{itemize}

\subsubsection{Measuring methods of brain waves from different parts of the head}
\begin{itemize}
 \item goal(s): Existing studies showed theoretical approaches to gatter brain waves with in-ear or behind-ear EEGs. The goal is to use this approaches and define requirements for building a small device to measure brain waves.
 \item description: In this package we attempt to define requirements for building a small device.
 \item expected results: Prove that brain waves can be measured from different head-parts than the forehead.
 \item responsible person: Neuroscience researcher
 \item dependencies: WP 1.2
 \item start date: 05.01.2016
 \item end date: 05.07.2016
\end{itemize}

\subsubsection{Survey of state of the art for sensors and devices for brain wave measurement}
\begin{itemize}
 \item goal(s): Analyse the hardware components of existing brain wave measurement and gather enough information to build a small device.
 \item description: There already exists a lot of sensors for detecting brain waves. Main part here is to look, if a device already exists or if we buy a existing one a make it smaller.
 \item expected results: Today do probably exist decent sensors, but none exactly as needed for the planned tiny device.
 \item responsible person: Hardware engineer
 \item dependencies: none
 \item start date: 05.01.2015
 \item end date: 05.01.2016
\end{itemize}

\subsection{Hardware and software development}
\begin{itemize}
 \item goal(s): Develop prototype hardware and software for showing the success.
 \item description: To show that authentication over brain waves works, we have to develop a hardware prototype. There different kinds of software we have to develop. First an algorithm to ensure fault tolerance and an interface for the communication with the device.
 \item expected results: The developed application shows a successfully communication with the device.
 \item responsible person: Hardware engineer
 \item dependencies: WP 1.2
 \item start date: 05.07.2016
 \item end date: 05.07.2017
\end{itemize}

\subsubsection{Reviewing of existing algorithms for detecting patterns in measured brain}
\begin{itemize}
 \item goal(s): To identify the thought of a person.
 \item description: It is possible that the same thought of a person can be shown different in the brain wave. For this case we need some patterns to confirm the measured brain waves.
 \item expected results: A working algorithm with good performance.
 \item responsible person: Computer science researcher
 \item dependencies: none
 \item start date: 05.07.2016
 \item end date: 05.10.2016
\end{itemize}

\subsubsection{Develop new algorithms for detecting patterns in measured brain waves}
\begin{itemize}
 \item goal(s):  Develop the needed algorithms.
 \item description: If there are no existing algorithms for detecting patterns in measured brain waves, which can be used in this project, then new ones need to be developed.
 \item expected results: Our algorithms need to be reliable and fast.
 \item responsible person: Computer science researcher
 \item dependencies: WP 2.1 
 \item start date: 05.10.2016
 \item end date: 05.01.2017
\end{itemize}

\subsubsection{Define the communication protocol and interface of the Wavy}
\begin{itemize}
 \item goal(s): A software interface for the Wavy
 \item description: Develop an software interface for other applications to communicate with the Wavy. This interface should operation system or other developers allow to handle their authentication over Wavy.
 \item expected results: A easy usable and reliable software interface implement for several programing languages.
 \item responsible person: Software engineer
 \item dependencies: none
 \item start date: 05.07.2016
 \item end date: 05.07.2017
\end{itemize}

\subsubsection{Develop small sensors for brain wave measurement}
\begin{itemize}
 \item goal(s): Develop small sensors for brain wave measurement so they can be placed in the Wavy.
 \item description: Because the Wavy should be build as tiny as possible small sensors are needed.
 \item expected results: This work results in a tiny fully functional sensor for surement.
 \item responsible person: Hardware engineer
 \item dependencies: WP 1.4
 \item start date: 05.07.2016
 \item end date: 05.01.2017
\end{itemize}

\subsubsection{Develop a microcontroller for the Wavy}
\begin{itemize}
 \item goal(s): A microcontroller to handle and identify brain waves.
 \item description: Develop a microcontroller thats manage the detection and identification of brain waves. It is working with the developed algorithm and sending it over a bluetooth interface to a chosen device. The communication with the controller is handled with the developed software interface.
 \item expected results: A working microcontroller.
 \item responsible person: Hardware engineer
 \item dependencies: WP 2.2, WP 2.3
 \item start date: 05.01.2017
 \item end date: 05.07.2017
\end{itemize}

\subsection{Prototype development}
\begin{itemize}
 \item goal(s): A device that is similar than the device for the consumer.
 \item description: Develop a prototype which can satisfy all requirements
 \item expected results:
 \begin{itemize}
  \item Wavy prototype
  \item Demonstration software
  \item A study confirming the superiority of our new method
 \end{itemize}
 \item responsible person: Hardware engineer
 \item dependencies: WP 2
 \item start date: 05.07.2017
 \item end date: 05.07.2018
\end{itemize}

\subsubsection{Create the Wavy prototype}
\begin{itemize}
 \item goal(s): Develop a wearable prototype.
 \item description: The Wavy prototype doesn’t have to be the final product but it should function like specified above.
 \item expected results: working prototype (Wavy)
 \item responsible person: Hardware engineer
 \item dependencies: WP 2
 \item start date: 05.07.2017
 \item end date: 05.03.2018
\end{itemize}

\subsubsection{Write a software prototype}
\begin{itemize}
 \item goal(s): Write a simple prototype including all essential features of WaveMeIn.
 \item description: The software prototype should implement the software, which is required for using the WaveMeIn Features.
 \item expected results: A small software to show how the Wavy device works (log in to an operation system).
 \item responsible person: Software engineer
 \item dependencies: WP 2
 \item start date: 05.07.2017
 \item end date: 05.03.2018
\end{itemize}

\subsubsection{Comparing with existing authentication methods}
\begin{itemize}
 \item goal(s): certificate, publicity
 \item description: An external research comparison.
 \item expected results: Confirm that the safety of this authentication method is superior to any other authentication method.
 \item responsible person: Computer science researcher
 \item dependencies: WP 2, WP 3.1
 \item start date: 05.03.2018
 \item end date: 05.07.2018
\end{itemize}

>>>>

\subsection*{WP 1 - Basic research}
\begin{itemize}
 \item goal(s): The goal of the research part is to clarify the scientific requirements, needed for the creation of the prototype.
 \item description: This work package deals with the brain waves related part of this project.
 \item expected results: Thought identification, confirmation of the uniqueness of brain waves, measuring brain waves from different body parts.
 \item responsible person: Neuroscience researcher
 \item dependencies: none
 \item start date: 05.01.2015
 \item end date: 05.07.2016
\end{itemize}

\subsubsection*{WP 1.1 - Confirm uniqueness of a person’s brain wave pattern}
\begin{itemize}
 \item goal(s): Confirm assumption of persons unique brain waves.
 \item description: Every person has an unique brain wave pattern for the same thought. This pattern can be used to identify the person.
 \item expected results: If the research shows unexpected results and it the uniqueness can’t be proved, it will limit the security aspect of the project, but it still can be realised.
 \item responsible person: Neuroscience researcher
 \item dependencies: none
 \item start date: 05.01.2015
 \item end date: 05.07.2015
\end{itemize}

\subsubsection*{WP 1.2 - Reliable thought identification}
\begin{itemize}
 \item goal(s): Confirmation of our assumption, that a thought of a person can be identified again as the same.
 \item description: Research on how a specific brain wave of a person can be identified reliably.
 \item expected results: A person can be identified again as the same.
 \item responsible person: Neuroscience researcher
 \item dependencies: WP 1.1
 \item start date: 05.07.2015
 \item end date: 05.01.2016
\end{itemize}

\subsubsection*{WP 1.3 - Measuring methods of brain waves from different parts of the head}
\begin{itemize}
 \item goal(s): Existing studies showed theoretical approaches to gatter brain waves with in-ear or behind-ear EEGs. The goal is to use this approaches and define requirements for building a small device to measure brain waves.
 \item description: In this package we attempt to define requirements for building a small device.
 \item expected results: Prove that brain waves can be measured from different head-parts than the forehead.
 \item responsible person: Neuroscience researcher
 \item dependencies: WP 1.2
 \item start date: 05.01.2016
 \item end date: 05.07.2016
\end{itemize}

\subsubsection*{WP 1.4 - Survey of state of the art for sensors and devices for brain wave measurement}
\begin{itemize}
 \item goal(s): Analyse the hardware components of existing brain wave measurement and gather enough information to build a small device.
 \item description: There already exists a lot of sensors for detecting brain waves. Main part here is to look, if a device already exists or if we buy a existing one a make it smaller.
 \item expected results: Today do probably exist decent sensors, but none exactly as needed for the planned tiny device.
 \item responsible person: Hardware engineer
 \item dependencies: none
 \item start date: 05.01.2015
 \item end date: 05.01.2016
\end{itemize}

\subsection*{WP 2 - Hardware and software development}
\begin{itemize}
 \item goal(s): Develop prototype hardware and software for showing the success.
 \item description: To show that authentication over brain waves works, we have to develop a hardware prototype. There different kinds of software we have to develop. First an algorithm to ensure fault tolerance and an interface for the communication with the device.
 \item expected results: The developed application shows a successfully communication with the device.
 \item responsible person: Hardware engineer
 \item dependencies: WP 1.2
 \item start date: 05.07.2016
 \item end date: 05.07.2017
\end{itemize}

\subsubsection*{WP 2.1 - Reviewing of existing algorithms for detecting patterns in measured brain}
\begin{itemize}
 \item goal(s): To identify the thought of a person.
 \item description: It is possible that the same thought of a person can be shown different in the brain wave. For this case we need some patterns to confirm the measured brain waves.
 \item expected results: A working algorithm with good performance.
 \item responsible person: Computer science researcher
 \item dependencies: none
 \item start date: 05.07.2016
 \item end date: 05.10.2016
\end{itemize}

\subsubsection*{WP 2.2 - Develop new algorithms for detecting patterns in measured brain waves}
\begin{itemize}
 \item goal(s):  Develop the needed algorithms.
 \item description: If there are no existing algorithms for detecting patterns in measured brain waves, which can be used in this project, then new ones need to be developed.
 \item expected results: Our algorithms need to be reliable and fast.
 \item responsible person: Computer science researcher
 \item dependencies: WP 2.1 
 \item start date: 05.10.2016
 \item end date: 05.01.2017
\end{itemize}

\subsubsection*{WP 2.3 - Define the communication protocol and interface of the Wavy}
\begin{itemize}
 \item goal(s): A software interface for the Wavy
 \item description: Develop an software interface for other applications to communicate with the Wavy. This interface should operation system or other developers allow to handle their authentication over Wavy.
 \item expected results: A easy usable and reliable software interface implement for several programing languages.
 \item responsible person: Software engineer
 \item dependencies: none
 \item start date: 05.07.2016
 \item end date: 05.07.2017
\end{itemize}

\subsubsection*{WP 2.4 - Develop small sensors for brain wave measurement}
\begin{itemize}
 \item goal(s): Develop small sensors for brain wave measurement so they can be placed in the Wavy.
 \item description: Because the Wavy should be build as tiny as possible small sensors are needed.
 \item expected results: This work results in a tiny fully functional sensor for surement.
 \item responsible person: Hardware engineer
 \item dependencies: WP 1.4
 \item start date: 05.07.2016
 \item end date: 05.01.2017
\end{itemize}

\subsubsection*{WP 2.5 - Develop a microcontroller for the Wavy}
\begin{itemize}
 \item goal(s): A microcontroller to handle and identify brain waves.
 \item description: Develop a microcontroller thats manage the detection and identification of brain waves. It is working with the developed algorithm and sending it over a bluetooth interface to a chosen device. The communication with the controller is handled with the developed software interface.
 \item expected results: A working microcontroller.
 \item responsible person: Hardware engineer
 \item dependencies: WP 2.2, WP 2.3
 \item start date: 05.01.2017
 \item end date: 05.07.2017
\end{itemize}

\subsection*{WP 3 - Prototype development}
\begin{itemize}
 \item goal(s): A device that is similar than the device for the consumer.
 \item description: Develop a prototype which can satisfy all requirements
 \item expected results:
 \begin{itemize}
  \item Wavy prototype
  \item Demonstration software
  \item A study confirming the superiority of our new method
 \end{itemize}
 \item responsible person: Hardware engineer
 \item dependencies: WP 2
 \item start date: 05.07.2017
 \item end date: 05.07.2018
\end{itemize}

\subsubsection*{WP 3.1 - Create the Wavy prototype}
\begin{itemize}
 \item goal(s): Develop a wearable prototype.
 \item description: The Wavy prototype doesn’t have to be the final product but it should function like specified above.
 \item expected results: working prototype (Wavy)
 \item responsible person: Hardware engineer
 \item dependencies: WP 2
 \item start date: 05.07.2017
 \item end date: 05.03.2018
\end{itemize}

\subsubsection*{WP 3.2 - Write a software prototype}
\begin{itemize}
 \item goal(s): Write a simple prototype including all essential features of WaveMeIn.
 \item description: The software prototype should implement the software, which is required for using the WaveMeIn Features.
 \item expected results: A small software to show how the Wavy device works (log in to an operation system).
 \item responsible person: Software engineer
 \item dependencies: WP 2
 \item start date: 05.07.2017
 \item end date: 05.03.2018
\end{itemize}

\subsubsection*{WP 3.3 - Comparing with existing authentication methods}
\begin{itemize}
 \item goal(s): certificate, publicity
 \item description: An external research comparison.
 \item expected results: Confirm that the safety of this authentication method is superior to any other authentication method.
 \item responsible person: Computer science researcher
 \item dependencies: WP 2, WP 3.1
 \item start date: 05.03.2018
 \item end date: 05.07.2018
\end{itemize}
